---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

All commands that you use to use when developing packages...

# First time just after creating the project

- Fill the following chunk to create the DESCRIPTION of your package

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Analyse the Activities of Squirrels of Central Park",
    Description = "This package provides tools to analyse the activities of squirrels of Central Park, NYC. The data is from the NYC Squirrel Census - raw data at NY Data portal.",
    `Authors@R` = c(
      person(given = "Margot", family = "Brard", role = c("aut", "cre"), email = "margot@thinkr.fr", comment = c(ORCID = "0000-0001-6754-0659")),
      person(given = "ThinkR", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Margot Brard")
```

# Start using git

```{r, eval=FALSE}
usethis::use_git()
# Deal with classical files to ignore
usethis::git_vaccinate()
# Use main for primary branch
usethis::git_default_branch_rename()
```

# Set extra sources of documentation

```{r, eval=FALSE}
# Install a first time
remotes::install_local()
# README
usethis::use_readme_rmd()
# Code of Conduct
usethis::use_code_of_conduct("contact@fake.com")
# NEWS
usethis::use_news_md()
```

**From now, you will need to "inflate" your package at least once to be able to use the following commands. Let's go to your flat template, and come back here later if/when needed.**


# Package development tools
## Use once

```{r, eval=FALSE}
# Pipe
usethis::use_pipe()

# package-level documentation
usethis::use_package_doc()

# GitHub
# Add your credentials for GitHub
gitcreds::gitcreds_set()
# Send your project to a new GitHub project
usethis::use_github()

# Set Continuous Integration
# _GitHub
usethis::use_github_action_check_standard()
usethis::use_github_action("pkgdown")
usethis::use_github_action("test-coverage")
# _GitLab
gitlabr::use_gitlab_ci(type = "check-coverage-pkgdown")

# Add new flat template
fusen::add_flat_template(template = "additional",
                         flat_name = "check_data")
```


## Data

```{r}
# data_act_squirrels
usethis::use_data_raw("data_act_squirrels") # create the dataset in this file
checkhelper::use_data_doc("data_act_squirrels")
rstudioapi::navigateToFile("R/data_act_squirrels.R") # create the documentation of the dataset
attachment::att_amend_desc() # update the documentation of the dataset

```

## Use everytime needed

```{r}
# Simulate package installation
pkgload::load_all()

# Generate documentation and deal with dependencies
attachment::att_amend_desc()

# Check the package
devtools::check()
```

# Code coverage

```{r}
covr::report()
```

# Share the package

```{r}
# set and try pkgdown documentation website
usethis::use_pkgdown()
pkgdown::build_site(override = list(destination = "inst/site"))

# build the tar.gz with vignettes to share with others
devtools::build(vignettes = TRUE)
remotes::install_local(path = "~/squirrels_0.0.0.9000.tar.gz") 
```

