---
title: "flat_check_data.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(ggplot2)
library(dplyr)
library(glue)
library(tools)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Check the values of a vector of primary fur colors

You can check if the column of primary fur color contains only allowed values with `check_primary_color_is_ok()`. 

Allowed values are "Gray", "Cinnamon", "Black", and missing values. If the column contains not allowed values, an explicit error message is displayed.

```{r function-check_primary_color_is_ok}
#' Check the values of a vector of primary fur colors
#'
#' @param string Character. A vector with the primary fur color.
#'
#' @return Boolean. TRUE if all colors are correct.
#' @export
#'
#' @examples
check_primary_color_is_ok <- function(string) {
  
  all_colors_OK <- all(
    string %in% c("Gray", "Cinnamon", "Black", NA)
  )
  
  if (isFALSE(all_colors_OK)) {
    stop('The vector of primary fur color contains not allowed colors. Colors should be among values "Gray", "Cinnamon", "Black", or missing values')
  }
  
  return(all_colors_OK)
}
```

```{r example-check_primary_color_is_ok}
check_primary_color_is_ok(string = c("Black", "Cinnamon", NA))
check_primary_color_is_ok(string = c("Gray", "Cinnamon", "Gray"))
```

```{r tests-check_primary_color_is_ok}
test_that("check_primary_color_is_ok works", {
  
  expect_true(check_primary_color_is_ok(string = c("Black", "Cinnamon", NA))) 
  
  expect_true(check_primary_color_is_ok(string = c("Gray", "Cinnamon", "Gray")))
  
  expect_error(check_primary_color_is_ok(string = c("Gray", "Cinnamon", "Blue")),
               regexp = "The vector of primary fur color contains not allowed colors")
  
})
```

# Check the integrity of the column of primary fur colors

You can check the integrity of the primary fur colors of a dataset with `check_squirrel_data_integrity()`. This function checks that the dataset contains a `primary_fur_color` variable, and that this column only contains allowed values ("Gray", "Cinnamon", "Black", and missing values).

```{r function-check_squirrel_data_integrity}
#' Check the integrity of the column of primary fur colors
#'
#' @param df_squirrels Data frame. A dataset with squirrels data.
#'
#' @return Nothing. Use for side effect. Displays a message if everything is ok
#' @export
#'
#' @examples
check_squirrel_data_integrity <- function(df_squirrels){
  
  # Check if there is a primary_fur_color column
  if (isFALSE("primary_fur_color" %in% names(df_squirrels))) {
    stop("There is no primary_fur_color in this dataset")
  }
  
  # Check if the values in the primary_fur_color column are ok
  primary_colors_ok <- check_primary_color_is_ok(df_squirrels$primary_fur_color)
  
  if (isTRUE(primary_colors_ok)){
    message("All primary fur colors are ok")
  }
  
}
```

```{r example-check_squirrel_data_integrity}
my_data_squirrels <- readr::read_csv(
  system.file("nyc_squirrels_sample.csv", package = "squirrels")
)
check_squirrel_data_integrity(my_data_squirrels)
```

# study_activity

```{r function-study_activity}
#' Study the activities of the squirrels given a primary fur color
#'
#' @param df_squirrels_act Data frame. A dataset with the activities of the squirrels. This dataset mush have at leat these 4 columns: "age", "primary_fur_color", "activity", "counts".
#' @param col_primary_fur_color Character. The color of the primary fur color of interest. Only the squirrels with this primary fur color will be considered in the analysis.
#' 
#' @importFrom dplyr filter
#' @importFrom ggplot2 ggplot aes geom_col scale_fill_manual labs
#' @importFrom magrittr %>% 
#'
#' @return A list of two named elements. The first one is the filtered table. The second one is the ggplot.
#' @export
#'
#' @examples
study_activity <- function(df_squirrels_act, col_primary_fur_color) {
  
  if(isFALSE(is.data.frame(df_squirrels_act))) {
    stop("df_squirrels_act is not a data frame")
  }
  
  if(isFALSE(is.character(col_primary_fur_color))) {
    stop("col_primary_fur_color is not a character vector")
  }
  
  
  table <- df_squirrels_act %>% 
    filter(col_primary_fur_color == primary_fur_color)
  
  graph <- table %>% 
    ggplot() +
    aes(x = activity, y = counts, fill = age) +
    geom_col() +
    labs(x = "Type of activity",
         y = "Number of observations",
         title = glue("Type of activity by age for {tolower(col_primary_fur_color)} squirrels")) +
    scale_fill_manual(name = "Age",
                      values = c("#00688B", "#00BFFF"))
  
  return(list(table = table, graph = graph))
}


```


```{r example-study_activity}
data(nyc_squirrels_dummy)
study_activity(df_squirrels_act = nyc_squirrels_dummy, 
               col_primary_fur_color =  "Black")
```



```{r tests-study_activity}
test_that("study_activity works", {
  expect_true(inherits(study_activity, "function")) 
})
```




```{r tests-check_squirrel_data_integrity}
test_that("check_squirrel_data_integrity works", {
  
  # Everything is ok
  my_data_squirrels <- readr::read_csv(system.file("nyc_squirrels_sample.csv", package = "squirrels"))
  
  expect_message(check_squirrel_data_integrity(my_data_squirrels), 
                 regexp = "All primary fur colors are ok") 
  
  # Error : no primary_fur_color column in the dataset
  my_data_squirrels_wrong_colname <- my_data_squirrels %>% 
    dplyr::rename(primary_color = primary_fur_color)
  
  expect_error(check_squirrel_data_integrity(my_data_squirrels_wrong_colname), 
               regexp = "There is no primary_fur_color in this dataset")
  
  # Error : not allowed colors in the primary_fur_color column
  my_data_squirrels_wrong_colors <- my_data_squirrels %>% 
    dplyr::mutate(primary_fur_color = stringr::str_to_lower(primary_fur_color))
  
  expect_error(check_squirrel_data_integrity(my_data_squirrels_wrong_colors), 
               regexp = "The vector of primary fur color contains not allowed colors")
  
})
```


# save_as_csv

```{r function-save_as_csv}

#' A function to save csv
#' @param dataset A data frame 
#' @param path_name A file path
#'
#' @return Doesn't eturn anything writes a file to disk
#' @importFrom tools file_ext
#' @importFrom utils  write.csv2
#'
#' @export
#' @examples
#' 
save_as_csv <- function(dataset, path_name){
  
  file_extension = file_ext(path_name)
  folder_exists = file.exists(dirname(path_name))
  
  if(file_extension != "csv"){
    
    stop("the extension of the file to create is not the right one")
    
  }
  if(isFALSE(inherits(dataset, "data.frame"))){
    
    
    stop("the function is not applied to a data.frame")
  }
  
  if(isFALSE(folder_exists)){
    
    
    stop("the path where the file should be saved does not exist")
    
  }
  
  write.csv2(dataset, file = path_name)
  
  return(path_name)
  
}


```




```{r example-save_as_csv}
library(dplyr)
# Create a temporary directory
my_temp_folder <- tempfile(pattern = "savecsv")
dir.create(my_temp_folder)

data(iris)
# ok: the .csv file is saved in the current project
iris %>% save_as_csv(file.path(my_temp_folder, "output.csv"))

# ok: the .csv file is saved and the file opens
iris %>% save_as_csv(file.path(my_temp_folder, "output.csv")) %>% browseURL() 
```




```{r tests-save_as_csv}
library(dplyr)
test_that("save_as_csv works", {
  my_temp_folder <- tempfile(pattern = "savecsv")
  expect_error(iris %>% save_as_csv(file.path(my_temp_folder, "output.xlsx")),
               regexp = "the extension of the file to create is not the right one")
  
  expect_error(NULL %>% save_as_csv(file.path(my_temp_folder, "output.csv")),
               regexp = "the function is not applied to a data.frame")
  
  expect_error(iris %>% save_as_csv(file.path(my_temp_folder, "does/no/exist.csv")) ,  
               regexp = "the path where the file should be saved does not exist")
  
})

```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_check_data.Rmd", 
               vignette_name = "Check data")
```

